OwO

### 2020-05-07 1-Introduction.tex
Add some minor fixes all round

Embedded devices can use these CNN based algorithms to analyze their surroundings in an environment where they can't rely on external predictions from the cloud. One of the most significant issues is that achieving scene understanding requires multiple classifiers to solve various tasks. For example, a camera-based self-driving car has numerous things it is interested in resolving using the video output of its cameras. The tasks could be, for example, finding and classifying other vehicles, traffic signs, road markings, predicting paths of vehicles, pedestrians, and other actors, understanding where it can move and finally producing the output of steering angle and acceleration. All these tasks have to be solved using the limited computing capability onboard the actor, and the inference time for them can't be too long in order to react to everything within a reasonable time frame. Here we have many tasks, and if every task requires its independent network to produce the outputs, and we cut down on the network sizes, the classifiers might be powerful enough to produce safe outputs. On the other hand, if we don't reduce the network sizes, our inference time might be too long for a real-time system. One way to possibly get a good compromise between inference time and model complexity is to use multi-task learning and weight sharing within the model to get a single model with multiple outputs and similar or better performance to individual classifiers.

>>>>

Embedded devices can use these CNN based algorithms to analyze their surroundings in an environment where they can't rely on external predictions from the cloud. One of the most significant issues is that achieving scene understanding requires multiple classifiers to solve various tasks. For example, a camera-based self-driving car has numerous things it is interested in resolving using the video output of its cameras. The tasks could be, for example, finding and classifying other vehicles, traffic signs, road markings, predicting paths of vehicles, pedestrians, and other actors, understanding where it can move, and finally deciding the steering angle and acceleration for the car with the information. All these tasks have to be solved using the limited computing capability onboard the actor, and the inference time for them can't be too long in order to react to everything within a reasonable time frame. Here we have many tasks, and if every task requires its independent network to produce the outputs, and we cut down on the network sizes, the classifiers might be powerful enough to produce safe outputs. On the other hand, if we don't reduce the network sizes, our inference time might be too long for a real-time system. One way to possibly get a good compromise between inference time and model complexity is to use multi-task learning and weight sharing within the model to get a single model with multiple outputs and similar or better performance to individual classifiers.

### 2020-05-07 3-Image-classification.tex
Add some minor fixes all round

ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand test images of the entire ImageNet dataset. In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train a deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.

@@

To give a formal definition of transfer learning, we will follow the definitions provided in \citep{transferSurvey2010}. Let $\mathcal{D}$ be a domain, which consists of a feature space $\mathcal{X}$ and a marginal probability distribution P($\mathcal{X}$). For a given domain, a task $\mathcal{T}$ = {$\mathcal{Y}$, f$\mathcal(X)$} consist of a label space $\mathcal{Y}$ for the inputs and of a predictive function $f(x)$ which produces predictions for all pairs ${x_i, y_i}$ where $x_i \in \mathcal{X}$ and $y_i \in \mathcal{Y}$. Given a source domain $\mathcal{D}_S$, a source task $\mathcal{T}_S$, a target domain $\mathcal{D}_T$ and a target task $\mathcal{T}_T$, where target and source are disjoint, transfer learning tries to improve the performance of $f_T(x)$ using $\mathcal{D}_S$ and $\mathcal{T}_S$.

@@

The idea behind transfer learning is to train on a related task to the end task first. Then the network weights in the model for the actual task are initialized to those of the model we are transferring from, so the training of the original model is a pre-step to the real task. Since training the models on ImageNet scale datasets is not generally feasible due to their large number of parameters and long training time, one of the pre-trained models is picked and then fine-tuned. Fine-tuning a classifier means taking the examples for the final task, and training the network on those, updating the original classifier at the same time. The transfer learning approach differs significantly from the traditional learning model, where each task requires a separate model that learns from the given data using random weights. Since image inputs are often very high dimensional, the traditional approach may not work in many cases. The pre-training allows for focusing on data that provides answers to the actual task and not on learning low-level features, which the ImageNet classifiers would already have learned.

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. Normally a mapping is learned between ${x}$ and ${y}$ using a function ${H(x)}$ but by the same token, we can learn a residual transformation, ${F(x) = H(x) - x}$, where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block ${y = F(x, \{W_i\}) + W_s x}$.

@@

The other approach to finding a better architecture is to use different kinds of blocks that are better. One way of finding better building blocks is by manual experimentation. The other, like in the case of MnasNet \citep{mnas}, is to pose the problem as an optimization problem and to use Neural Architecture Search \citep{neuralSearch} to find the optimal solution. In the case of MnasNet, the goal is to maximize m in ${ACC(m) \times [\frac{LAT(m)}{T}]^w}$, where ${T}$ is the target, by searching in a constrained space. So the goal is to optimize the accuracy with a given latency on a specific device. The search produces small but very efficient models when the target device is a mobile phone.

\section{EfficientNet}
EfficientNet models form a family of models ranging from EfficientNet0 to EfficientNet7 that were generated by smartly scaling existing convolutional models to optimize them for efficiency in a similar way to MnasNet \citep{efficientNet}. The more complex models are created by using compound scaling on the EfficientNet0 model, shown in Figure 3.3 (e),  where the width, depth, and the resolution of the network are scaled using a factor ${\phi}$. As the cost of neural architecture search grows exponentially as the size of the network grows, the search is only done on the base model. The search of ${\phi}$ is a constrained optimization problem, where width, depth and, resolution are constrained such that ${d^\phi \times w^\phi \times r^\phi \approx 2}$ and each increase in ${\phi}$ increases network FLOPS by ${2^\phi}$. The architecture search for the base network is similar to that of MnasNet. The target of EfficinetNet is  ${ACC(m) \times [\frac{FLOPS(m)}{T}]^w}$, so the goal is to optimize for both accuracy and number of floating-point operations instead of latency as in MnasNet \citep{efficientNet}.

As seen in figure 3.1, these optimizations allow for the EfficientNet to form a very performant architecture using a low amount of parameters that does well on ImageNet and is good at Transfer Learning also. Interestingly though, the reduction in FLOPS and parameters do not directly translate to low real-world inference time. As is compared in the paper, an EfficientNet-B1 gets a 5.7x speedup over a ResNet-152, while the EfficientNet scores significantly higher on ImageNet. So in terms of the time and accuracy ratio, the EfficientNet seems to do well. When looking at the inference time in terms of FLOPS and parameters, we can find out that the ResNet would be more efficient, as the ResNet has 7.6x as many parameters and 16x FLOPS when compared to the EfficientNet, but the inference time multiplier is 5.7x. From this comparison, we can easily see that the number of FLOPS is not a direct proxy for inference time and instead the optimization should be for latency directly as in MnasNet if that is the goal.

The proposed EfficientNet models use mobile inverted bottleneck (MBConv) blocks used in MobileNetV2 \citep{mobileNetv2} in constructing the base model. The MobileNet uses a Depthwise Separable Convolution, where a depthwise convolution and a pointwise convolution are applied in sequence. The depthwise convolution applies ${d_i}$ ${k x k}$ filters to the input, where ${d_i}$ is the input channels and ${k}$ is the kernel size leading to an output channel count ${d_j = d_i}$. A normal convolutional layer would apply multiple filters having ${M}$ channels with the computational cost of ${h_i w_i d_i d_j k^2}$, whereas the depthwise convolution only has a cost of ${h_i w_i d_i (k^2 + d_j)}$, reducing the cost by ${k^2}$. The result of the depthwise convolution then runs through a pointwise convolution, where a ${1 \times 1 \times d_j}$ 1d convolution is applied to get the final output as a linear combination of the channels. The inverted residuals in MBConv are connections similar to ResNet, but in this case they are connected between the low dimensional layers.

>>>>

ImageNet \citep{imagenet} has been one of the most significant data sets for image classification, producing several significant improvements to modern computer vision techniques.
The ImageNet challenge \citep{ILSVRC} is a competition consisting of a selected collection of 1000 classes and a total of 1.2 million training images and 150 thousand test images from the ImageNet data set.
Winning models from the ImageNet competition have provided some of the essential architectures modern computer vision algorithms use.
In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.

@@

To give a formal definition of transfer learning, we will follow the definitions provided in \citep{transferSurvey2010}.
Let $\mathcal{D}$ be a domain, which consists of a feature space $\mathcal{X}$ and a marginal probability distribution P($\mathcal{X}$).
For a given domain,a task T \[\mathcal{T} = \{\mathcal{Y}, f\mathcal(X)\}\] \noindent consists of a label space $\mathcal{Y}$ for the inputs and of a predictive function $f(x)$ which produces predictions for all pairs \{$x_i, y_i$\} where $x_i \in \mathcal{X}$ and $y_i \in \mathcal{Y}$.
Given a source domain $\mathcal{D}_S$, a source task $\mathcal{T}_S$, a target domain $\mathcal{D}_T$ and a target task $\mathcal{T}_T$, where target and source are disjoint, transfer learning tries to improve the performance of $f_T(x)$ using $\mathcal{D}_S$ and $\mathcal{T}_S$.

@@

The idea behind transfer learning is to train on a task that would produce useful features in solving some other task.
Then the network weights in the model for the actual task are initialized to those of the model we are transferring from, so the training of the original model is a pre-step to the real task.
Since training the models on ImageNet scale datasets is not generally feasible due to their large number of parameters and long training time, one of the pre-trained models is picked and then fine-tuned.
Fine-tuning a classifier means that some existing model is used as a weight initializer, and the network is then trained on the data of another task, updating the weights of the original classifier to better align with the new task.
The transfer learning approach differs significantly from the traditional learning model, where each task requires a separate model that learns from the given data using random weights.
Since image inputs are often very high dimensional, the traditional approach may not work in many cases.
The pre-training allows for focusing on data that provides answers to the actual task and not on learning low-level features, which the ImageNet classifiers would already have learned.

@@

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. Normally a mapping is learned between ${x}$ and ${y}$ using a function ${H(x)}$ but by the same token, we can learn a residual transformation, \[{F(x) = H(x) - x}\] \noindent where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block. \[y = F(x, \{W_i\}) + W_s x\]

@@

The other approach to finding a better architecture is to use different kinds of blocks that are better. One way of finding better building blocks is by manual experimentation. The other, like in the case of MnasNet \citep{mnas}, is to pose the problem as an optimization problem and to use Neural Architecture Search \citep{neuralSearch} to find the optimal solution. In the case of MnasNet, the goal is to maximize m in \[ACC(m) \times [\frac{LAT(m)}{T}]^w \] \noindent where ${T}$ is the target, by searching in a constrained space. So the goal is to optimize the accuracy with a given latency on a specific device. The search produces small but very efficient models when the target device is a mobile phone.

\section{EfficientNet}
EfficientNet models form a family of models ranging from EfficientNet0 to EfficientNet7 that were generated by smartly scaling existing convolutional models to optimize them for efficiency in a similar way to MnasNet \citep{efficientNet}.
The more complex models are created by using compound scaling on the EfficientNet0 model, shown in Figure 3.3 (e),  where the width, depth, and the resolution of the network are scaled using a factor ${\phi}$.
As the cost of neural architecture search grows exponentially as the size of the network grows, the search is only done on the base model.
The search of ${\phi}$ is a constrained optimization problem, where width, depth and, resolution are constrained such that ${d^\phi \times w^\phi \times r^\phi \approx 2}$ and each increase in ${\phi}$ increases network FLOPS by ${2^\phi}$.
The architecture search for the base network is similar to that of MnasNet. The target of EfficinetNet is  \[ACC(m) \times [\frac{FLOPS(m)}{T}]^w\] \noindent so the goal is to optimize for both accuracy and number of floating-point operations instead of latency as in MnasNet \citep{efficientNet}.

As seen in figure 3.1, these optimizations allow for the EfficientNet to form a very performant architecture using a low amount of parameters that does well on ImageNet and is good at Transfer Learning also. Interestingly though, the reduction in FLOPS and parameters do not directly translate to low real-world inference time. As is compared in the paper, an EfficientNet-B1 gets a 5.7x speedup over a ResNet-152, while the EfficientNet scores significantly higher on ImageNet. So in terms of the time and accuracy ratio, the EfficientNet seems to do well. When looking at the inference time in terms of FLOPS and parameters, we can find out that the ResNet would be more efficient, as the ResNet has 7.6x as many parameters and 16x FLOPS when compared to the EfficientNet, but the inference time multiplier is 5.7x. From this comparison, we can easily see that the number of FLOPS is not a direct proxy for inference time.
Instead, the optimization should be for latency directly as in MnasNet if that is the goal.

The proposed EfficientNet models use mobile inverted bottleneck (MBConv) blocks used in MobileNetV2 \citep{mobileNetv2} in constructing the base model. The MobileNet uses a Depthwise Separable Convolution, where a depthwise convolution and a pointwise convolution are applied in sequence. The depthwise convolution applies ${d_i}$ ${k x k}$ filters to the input, where ${d_i}$ is the input channels and ${k}$ is the kernel size leading to an output channel count ${d_j = d_i}$. A normal convolutional layer would apply multiple filters having ${M}$ channels with the computational cost of ${h_i w_i d_i d_j k^2}$, whereas the depthwise convolution only has a cost of ${h_i w_i d_i (k^2 + d_j)}$, reducing the cost by ${k^2}$. The result of the depthwise convolution then runs through a pointwise convolution, where a ${1 \times 1 \times d_j}$ 1d convolution is applied to get the final output as a linear combination of the channels. The inverted residuals in MBConv are connections similar to ResNet, but in this case, they are connected between the low dimensional layers.
